---
title: "IPEF"
author: "Bruce Peng"
date: "14 October 2019"
output: html_document
---

Below are the analyses for IPEF

**Participants and trial numbers:**
A total of 40 participants are included in this dataset, each participants completed 30 trials thus the total number of trials is 40x30= 1200. 36 trials were deleted due to written description not matching the condition requirement or other issues. Thus, the total number of trials = 1164.

**Data description:**
*participant:* N=40 
*Gender* Gender of the participant
*Face_gender* Gender of the face presented with each story
*Story_ID:* Story presented to participants on each trial, a total of 30 stories were presented. These stories can be found in IPEF_stimuli.xlsx
*Faces_ID* Individual face presneted with each story on each trial, a total of 30 faces were used. These can be found in IPEF_stimuli.xlsx
*Trial:* Trial order presented to participant.
*Condition:* Imagine helping (Experimental:Imagine),Estimate helping (Control:Estimate) and identify journalistic technique (Control:Identify)
*Detail.response:* The imagined media website/scene in your mind was? (collected for estimate and imagine helping conditions). Responses were made on a 1(simple)-7(detailed) Likert scale. 
*Coherence.response:*The imagined media website/scene in your mind was? (collected for estimate and imagine helping conditions). Responses were made on a 1(vague)-7(coherent and clear) Likert scale. 
*Perspective.response:*  When you identified the media website, imagined helping, or visualized the media website and comments  did you consider  the thoughts and feelings of the person? (collected for all conditions). Responses are made on a 1(not at all)- 7 (strongly considered). 
*Help.response:* Main DV of interest. How likely would you be to help in this situation? (collected for all conditions). Responses are made on a 1(not at all)- 7 (very willing).
*Emotional reaction:*
Emotional reaction (collected for all conditions) rated on a 1(not at all)-7(very strongly) Likert scale for the following emotions:
-	Intrigued
-	Soft-hearted
-	Troubled 
-	Warm 
-	Distressed
-	Sympathetic
-	Intent
-	Compassionate
-	Disturbed
-	Tender
-	Moved
-	Worried
Note emotional concern refers to 6 measures (i.e. sympathy, compassion, moved, tendered, soft-hearted and warm), the 12 measures were used to mask these 6 measures to minimize participants’ awareness of the emotional concern measures. 
*IRI components:* Participants level responses for the IRI (each item is rated on a A(doesn't describe me well)- E (describe me well) Likert scale), each participant has an averaged score of the following 4 components
- Perspective_taking
- Fantasy
- Emotional_concern
- Personal_distress

#Package and directory set up
```{r, include=FALSE}
#Obtain necessary packages
if (!require(sjstats)) install.packages('sjstats')
if (!require(sjPlot)) install.packages('sjPlot')
#if (!require(sjmisc)) install.packages('sjmisc')
if (!require(lme4)) install.packages('lme4')
if (!require(lmerTest)) install.packages('lmerTest')
if (!require(lattice)) install.packages('lattice')
if (!require(mediation)) install.packages('mediation')
if (!require(ggeffects)) install.packages('ggeffects')
if (!require(emmeans)) install.packages('emmeans')
if (!require(lavaan)) install.packages('lavaan')
if (!require(simr)) install.packages('simr')
if (!require(reshape)) install.packages('reshape')
if (!require(tidyverse)) install.packages('tidyverse')
if (!require(MuMIn)) install.packages('MuMIn')
```
```{r setup, include=FALSE}
#Load packages
library(sjstats)
library (MuMIn)
library(sjPlot)
library(sjmisc)
library (lme4)
library(lmerTest)
library (lattice)
library (mediation)
library (emmeans)
library(ggeffects)
library(lavaan)
library(simr)
library(reshape)
library (tidyverse)
#set working directory
#setwd('G:/My Drive/Phd (1)/Experiment/Studies/Data/IPE/IPEF/IPEF_data/IPEF_analysis/')
setwd('C:/Users/bruce/Google Drive/Phd (1)/Experiment/Studies/Data/IPE/IPEF/IPEF_data/IPEF_analysis/')
#source custom functions
source("source/group_center.R")
source("source/Plot_LMM.R")
source("source/means.R")
source('http://faculty.missouri.edu/huangf/data/mcfa/mcfa.R')
```

#Data setup
*Loading data 
```{r}
#Main data
IPEF.df<- read.csv('IPEF_fulldata_N=40.csv', header=T)
IPEF.df$Story_ID<- as.factor(IPEF.df$Story_ID)
IPEF.df$Condition<- as.factor(IPEF.df$Condition)
levels (IPEF.df$Condition) <- c('Identify', 'Estimate', 'Imagine')
#IRI 
IPEF.IRI<- read.csv('IPEF_IRI.csv', header=T)
#create the 4 IRI components
IPEF.IRI <-IPEF.IRI%>% 
              mutate(
                IRIPerspective= (IRI3+IRI8+IRI11+IRI15+IRI21+IRI25+IRI28)/7,
                IRIFantasy =(IRI1+IRI5+IRI7+IRI12+IRI16+IRI23+IRI26)/7,
                IRIEmotional=(IRI2+IRI4+IRI9+IRI14+IRI18+IRI20+IRI22)/7,
                IRIDistress= (IRI6+IRI10+IRI13+IRI17+IRI19+IRI24+IRI27)/7)
#impute IRI Component scores into IPEF.df
start<-1;IRI_n<-1
for (x in seq(30,1200,by=30)){
  IPEF.df$IRIPerspective[start:x]<-rep(IPEF.IRI$IRIPerspective[IRI_n], 30)
  IPEF.df$IRIFantasy[start:x]<-rep(IPEF.IRI$IRIFantasy[IRI_n], 30)
  IPEF.df$IRIEmotional[start:x]<-rep(IPEF.IRI$IRIEmotional[IRI_n], 30)
  IPEF.df$IRIDistress[start:x]<-rep(IPEF.IRI$IRIDistress[IRI_n], 30)
  start<- x+1;IRI_n<-IRI_n+1
}
#remove trials deleted due to written responses
IPEF.df<- IPEF.df[complete.cases(IPEF.df$Condition),]
#Centring
IPEF.df<- IPEF.df%>% 
              mutate(
                #Create dummy variables
                dummy_ident=as.numeric(Condition=='Identify'),
                dummy_img= as.numeric(Condition=='Imagine'),
                dummy_est= as.numeric(Condition=='Estimate'),
                #Effect code Gender varaibles
                Gender_C = ifelse (Gender=='F',1, -1),
                Face_gender_C= ifelse(Face_gender=='F', 1, -1),
                #Create scene imagery measure
                Scene=(Coherence.response+Detail.response)/2,        
                #Within-cluster centering
                Scene_C= group_center(Scene,participant),
                Coherence_C=group_center(Coherence.response,participant),
                Detail_C=group_center(Detail.response,participant),
                Perspective_C =group_center(Perspective.response,participant),
                #Grand mean centring IRI component scores 
                IRIPerspective_GMC= IRIPerspective - mean(IPEF.IRI$IRIPerspective),
                IRIFantasy_GMC= IRIFantasy - mean (IPEF.IRI$IRIFantasy),
                IRIEmotional_GMC= IRIEmotional - mean (IPEF.IRI$IRIEmotional),
                IRIDistress_GMC=IRIDistress - mean(IPEF.IRI$IRIDistress))
#Create data file that only include conceptual helping and imagine condition. This is utilizied for interaction analyses (scene imagery*Condition) and multilevel moderated mediation analysis
interaction.df<- IPEF.df%>%
                      filter(Condition!='Identify')%>%
                      mutate(Perspective_C =group_center(Perspective.response,participant))
interaction.df$Condition<- droplevels(interaction.df$Condition)


```

#Main effect analyses: Replication of prosocial simulation effect
##Determine if clustering exists for story ID and participants
```{r}
null_full<- lmer(help.response~(1|participant)+(1|Story_ID)+(1|Faces_ID)+(1|Story_ID:Faces_ID), data=IPEF.df)
ranova(null_full)#significant so should include story and participant as a random effect, however face ID was not significant
```

##Prosoical simulation effect
```{r}
# follow the parsimonious mixed model approach described by Bates 2015 which involve fitting a maximual model first the iteratively reduce random effect dimension to find the best model.
zcp_model<- lmer(help.response~Condition+Gender_C*Face_gender_C+(dummy_est+dummy_img||participant)+(dummy_est+dummy_img||Story_ID), data= IPEF.df)
step(zcp_model)#retain dummy_img in participant
zcp_model_rm<- lmer(help.response~Condition+Gender_C*Face_gender_C+(dummy_img||participant)+(1|Story_ID), data= IPEF.df)

#add in correlation parameter
final_model<- lmer(help.response~Condition+Gender_C*Face_gender_C+(dummy_img|participant)+(1|Story_ID), data= IPEF.df)
final_model<-update(final_model, .~., start= getME(final_model, 'theta')) #one refit
anova(zcp_model_rm,final_model, refit=F)
anova(final_model, test='kenward-roger')
```

###Post hoc comparison
```{r}
emmeans(final_model, pairwise~Condition, adjust= 'bonferroni')
```
###Plots
```{r}
#Condition difference in willingness to help
ggpredict(final_model, c('Condition'))%>% plot()
#assess random effect relative to the means random effect
plot_model(final_model, type= 're')
#Identify as reference group
final_model2<- lmer(help.response~dummy_est+dummy_img+(dummy_img|participant)+(1|Story_ID), data= IPEF.df)
Plot_LMM(final_model2, 'Identify', 'Estimate', 'Imagine',1)
Plot_LMM(final_model2, 'Identify', 'Estimate', 'Imagine',2)
Plot_LMM(final_model2, 'Identify', 'Estimate', 'Imagine',3)
Plot_LMM(final_model2, 'Identify', 'Estimate', 'Imagine',4)
#Imagine as reference group
final_model3<- lmer(help.response~dummy_ident+dummy_img+(dummy_img|participant)+(1|Story_ID), data= IPEF.df)
Plot_LMM(final_model3, 'Estimate', 'Identify', 'Imagine',1)
Plot_LMM(final_model3, 'Estimate', 'Identify', 'Imagine',2)
Plot_LMM(final_model3, 'Estimate', 'Identify', 'Imagine',3)
Plot_LMM(final_model3, 'Estimate', 'Identify', 'Imagine',4)
```
###Assumption testing
```{r}
plot_model(final_model, type='diag')
```
###Effect size
```{r}
r.squaredGLMM(final_model)
```
###Power analysis
```{r}
pcurve_main <- powerCurve(final_model, test=fcompare(help.response~1), along='participant')
plot(pcurve_main)
```

#Interaction analysis: Condition(estimate vs imagine)* Vividness measures. 
##Detail & Coherence
```{r}
#Detail
int_zcp_det<- lmer (help.response~Condition*Detail_C+Gender_C*Face_gender_C+(dummy_img*Detail_C||participant)+ (dummy_img*Detail_C||Story_ID),data= interaction.df)
step(int_zcp_det)# Retain dummy_img and Detail_c in participant
int_rm_det<- lmer (help.response~Condition*Detail_C+Gender_C*Face_gender_C+(dummy_img+Detail_C||participant)+(1|Story_ID),data= interaction.df)
int_rm_det<-update(int_rm_det, .~., start= getME(int_rm_det, 'theta')) #one refit
##Final model
int_final_det<- lmer (help.response~Condition*Detail_C+Gender_C*Face_gender_C+(dummy_img+Detail_C|participant)+(1|Story_ID),data= interaction.df)
int_final_det<-update(int_final_det, .~., start= getME(int_final_det, 'theta')) #one refit
anova(int_rm_det,int_final_det, refit=F)
anova(int_final_det, test='kenward-roger')
summary(int_final_det)

#Coherence
int_zcp_coh<- lmer (help.response~Condition*Coherence_C+Gender_C*Face_gender_C+(dummy_img*Coherence_C||participant)+(dummy_img*Coherence_C||Story_ID),data= interaction.df)
step(int_zcp_coh) #Retain Coherence_C and Dummy_img in participant
int_rm_coh<- lmer (help.response~Condition*Coherence_C+Gender_C*Face_gender_C+(dummy_img+Coherence_C||participant)+ (1|Story_ID),data= interaction.df)
int_rm_coh<- update(int_rm_coh, .~., start= getME(int_rm_coh, 'theta')) #one refit
#add in correlation parameters: one at a time
int_final_coh<- lmer (help.response~Condition*Coherence_C+Gender_C*Face_gender_C+(dummy_img+Coherence_C|participant)+(1|Story_ID),data= interaction.df)
anova(int_rm_coh,int_final_coh, refit=F)
anova(int_final_coh, test='kenward-roger')
summary(int_final_coh)
```

###Plot the effect
```{r}
#Detail
sd<-sd(interaction.df$Detail_C);m<-mean(interaction.df$Detail_C)
m-sd;m;m+sd;
ggpredict(int_final_det, c("Condition","Detail_C [-1.26,0,1.26]"))%>% plot()
ggpredict(int_final_det, c("Detail_C[-1.26,0,1.26]","Condition"))%>% plot()
#Coherence
sd<-sd(interaction.df$Coherence_C);m<-mean(interaction.df$Coherence_C)
m-sd;m;m+sd;
ggpredict(int_final_coh, c("Condition","Coherence_C [-1.19,0,1.19]"))%>% plot()
ggpredict(int_final_coh, c("Coherence_C[-1.19,0,1.19]","Condition"))%>% plot()
```
###Assumption testing
```{r}
#Detail
plot_model(int_final_det, type='re')
plot_model(int_final_det, type='diag')
#Coherence
plot_model(int_final_coh, type='re')
plot_model(int_final_coh, type='diag')
```

###Effect size calculation
```{r}
#Detail
r.squaredGLMM(int_final_det)
#Coherence
r.squaredGLMM(int_final_coh)
```
###Power analysis
```{r}
#Detail 
pcurvedet <- powerCurve(power_det, test=fcompare(help.response~Condition+Detail_C), along='Participant')
plot(pcurvedet)
#Coherence
pcurve_coh <- powerCurve(int_final_coh, test=fcompare(help.response~Condition+Coherence_C), along='Participant')
plot(pcurve_coh)
```

#Multilevel Mediation analysis
Perspective taking
##Path a
```{r}
detach (package:lmerTest, unload=T)
library(lmerTest)
#Identify vs Imagine:path a
med.fit_0v2_zcp<- lmer(Perspective.response~dummy_est +dummy_img +Gender_C*Face_gender_C+(dummy_est +dummy_img||participant), data= IPEF.df)
step(med.fit_0v2_zcp) #retain all
##Final model
med.fit_0v2_final<- lmer(Perspective.response~dummy_est +dummy_img+Gender_C*Face_gender_C+(dummy_est +dummy_img|participant), data= IPEF.df)
med.fit_0v2_final<-update(med.fit_0v2_final, .~., start= getME(med.fit_0v2_final, 'theta'))#one refit
anova(med.fit_0v2_zcp,med.fit_0v2_final, refit=F)
summary(med.fit_0v2_final)

#Estimate vs Imagine:path a
med.fit_1v2_zcp<- lmer(Perspective.response~dummy_ident +dummy_img +Gender_C*Face_gender_C+(dummy_ident +dummy_img||participant), data= IPEF.df)
step(med.fit_1v2_zcp)#retain all
##Final Model
med.fit_1v2_final<- lmer(Perspective.response~dummy_ident +dummy_img +Gender_C*Face_gender_C+(dummy_ident +dummy_img|participant), data= IPEF.df)
med.fit_1v2_final<-update(med.fit_1v2_final, .~., start= getME(med.fit_1v2_final, 'theta'))#five refit
anova(med.fit_1v2_zcp,med.fit_1v2_final, refit=F)
summary(med.fit_1v2_final)
```
##Path b and c'
```{r}
#Identify vs Imagine:path b and c'
out.fit_0v2_zcp<- lmer(help.response~dummy_est +dummy_img +Perspective_C+Gender_C*Face_gender_C+(dummy_est +dummy_img +Perspective_C||participant), data= IPEF.df)
step(out.fit_0v2_zcp) #retain all
##Final model
out.fit_0v2_final<- lmer(help.response~dummy_est +dummy_img +Perspective_C+Gender_C*Face_gender_C+(dummy_est+dummy_img|participant), data= IPEF.df) #remove Perspective_C (smallest varaince) due to convergence failure
anova(out.fit_0v2_zcp,out.fit_0v2_final, refit=F)
summary(out.fit_0v2_final)

#Estimate vs Imagine:path b and c'
out.fit_1v2_zcp<- lmer(help.response~dummy_ident +dummy_img +Perspective_C+Gender_C*Face_gender_C+(dummy_ident +dummy_img +Perspective_C||participant), data= IPEF.df)
step(out.fit_1v2_zcp)#remove dummy_ident
#Final model
out.fit_1v2_final<- lmer(help.response~dummy_ident +dummy_img +Perspective_C+Gender_C*Face_gender_C+(Perspective_C +dummy_img |participant), data= IPEF.df) 
out.fit_1v2_final<-update(out.fit_1v2_final, .~., start= getME(out.fit_1v2_final, 'theta')) #fitted after one refit.
summary(out.fit_1v2_final)
```
##Mediation model
```{r}
#Identify vs Imagine
med.out_0v2 <- mediate (med.fit_0v2_final, out.fit_0v2_final, treat='dummy_img', mediator = 'Perspective_C')
summary(med.out_0v2);plot(med.out_0v2)
#Estimate vs Imagine
med.out_1v2 <- mediate (med.fit_1v2_final, out.fit_1v2_final, treat='dummy_img', mediator = 'Perspective_C')
summary(med.out_1v2);plot(med.out_1v2)
#Exploratory Identify vs Estimate
med.out_0v1 <- mediate (med.fit_0v2_final, out.fit_0v2_final, treat='dummy_est', mediator = 'Perspective_C')
summary(med.out_0v1);plot(med.out_0v1)
```
#Multilevel moderated mediation
###Detail
```{r}
library(lmerTest)
detach (package:lmerTest, unload=T)
interaction.df$imgdet_int<- interaction.df$dummy_img*interaction.df$Detail_C
#Mediation effect across the two conditons
med.fit_det <- lmer (Perspective.response~dummy_img*Detail_C+Gender_C*Face_gender_C+(dummy_img+Detail_C|participant) ,data= interaction.df)
med.fit_det<-update(med.fit_det, .~., start= getME(med.fit_det, 'theta'))#one refit
out.fit_det<- lmer (help.response~dummy_img*Detail_C+Perspective_C+Gender_C*Face_gender_C+(dummy_img+dummy_img:Detail_C+Perspective_C|participant),data= interaction.df)
out.fit_det<-update(out.fit_det, .~., start= getME(out.fit_det, 'theta'))#4 refit
Mod.Med_Detest <- mediate(med.fit_det, out.fit_det, covariates = list(dummy_img = 0), treat="Detail_C", mediator="Perspective_C")
Mod.Med_Detimg <- mediate(med.fit_det, out.fit_det,covariates = list(dummy_img = 1), treat="Detail_C", mediator="Perspective_C")
#Moderated mediation analysis
med.fit_det2 <- lmer (Perspective.response~dummy_img+Detail_C+imgdet_int+Gender_C*Face_gender_C+(dummy_img+Detail_C|participant) ,data= interaction.df)
med.fit_det2<-update(med.fit_det2, .~., start= getME(med.fit_det2, 'theta'))#one refit
out.fit_det2<- lmer (help.response~dummy_img+Detail_C+imgdet_int+Perspective_C+Gender_C*Face_gender_C+(dummy_img+imgdet_int+Perspective_C|participant),data= interaction.df) 
out.fit_det2<-update(out.fit_det2, .~., start= getME(out.fit_det2, 'theta'))#4 refit
med.out_det <- mediate (med.fit_det2, out.fit_det2, treat='imgdet_int', mediator = 'Perspective_C')
summary(Mod.Med_Detest);summary(Mod.Med_Detimg);summary(med.out_det)
summary(med.fit_det);summary(out.fit_det)
#used to plot path a and c'
img_DP <- lmer (Perspective.response~dummy_est*Detail_C+Gender_C*Face_gender_C+(dummy_est+Detail_C|participant) ,data= interaction.df)
img_HP <- lmer (Perspective.response~dummy_est*Detail_C+Gender_C*Face_gender_C+(dummy_est+Detail_C|participant) ,data= interaction.df)
summary(img_DP);summary(img_HP)
```

##Coherence
```{r}
library(lmerTest)
detach (package:lmerTest, unload=T)
#below only inlcude parsimonious model
interaction.df$imgcoh_int<- interaction.df$dummy_img*interaction.df$Coherence_C
#Mediation effect across the two conditons
med.fit_coh <- lmer (Perspective.response~dummy_img*Coherence_C+Gender_C*Face_gender_C+(dummy_img+Coherence_C|participant),data= interaction.df)
med.fit_coh<-update(med.fit_coh, .~., start= getME(med.fit_coh, 'theta'))#one refit
out.fit_coh<- lmer (help.response~dummy_img*Coherence_C+Perspective_C+Gender_C*Face_gender_C+(dummy_img+Perspective_C|participant),data= interaction.df) 
Mod.Med_Cohest <- mediate(med.fit_coh, out.fit_coh, covariates = list(dummy_img = 0), treat="Coherence_C", mediator="Perspective_C")
Mod.Med_Cohimg <- mediate(med.fit_coh, out.fit_coh, covariates = list(dummy_img = 1), treat="Coherence_C", mediator="Perspective_C")
#Moderated mediation analysis
med.fit_coh2 <- lmer (Perspective.response~dummy_img+Coherence_C+imgcoh_int+Gender_C*Face_gender_C+(dummy_img+Coherence_C|participant),data= interaction.df)
med.fit_coh2<-update(med.fit_coh2, .~., start= getME(med.fit_coh2, 'theta'))#one refit
out.fit_coh2<- lmer (help.response~dummy_img+Coherence_C+Perspective_C+imgcoh_int+Gender_C*Face_gender_C+(dummy_img+Perspective_C|participant),data= interaction.df) med.out_coh <- mediate (med.fit_coh2, out.fit_coh2, treat='imgcoh_int', mediator = 'Perspective_C')
summary(Mod.Med_Cohest);summary(Mod.Med_Cohimg);summary(med.out_coh)
summary(med.fit_coh);summary(out.fit_coh)
#use to plot path a
est_cohpersp<- lmer (Perspective.response~Coherence_C+Gender_C*Face_gender_C+(Coherence_C|participant),data= subset(interaction.df,Condition=="Estimate"))
img_cohpersp<- lmer (Perspective.response~Coherence_C+Gender_C*Face_gender_C+(Coherence_C|participant),data= subset(interaction.df,Condition=="Imagine"))
summary(est_cohpersp);summary(img_cohpersp)
```
##Scene
```{r}
library(lmerTest)
detach (package:lmerTest, unload=T)
#below only inlcude parsimonious model
interaction.df$imgscene_int<- interaction.df$dummy_img*interaction.df$Scene_C
#Mediation effect across the two conditons
med.fit_scene <- lmer (Perspective.response~dummy_img*Scene_C+Gender_C*Face_gender_C+(dummy_img|participant),data= interaction.df)
out.fit_scene<- lmer (help.response~dummy_img*Scene_C+Perspective_C+Gender_C*Face_gender_C+(dummy_img+Perspective_C|participant),data= interaction.df) 
Mod.Med_sceneest <- mediate(med.fit_scene, out.fit_scene, covariates = list(dummy_img = 0), treat="Scene_C", mediator="Perspective_C")
Mod.Med_sceneimg <- mediate(med.fit_scene, out.fit_scene, covariates = list(dummy_img = 1), treat="Scene_C", mediator="Perspective_C")
#Moderated mediation analysis
med.fit_scene2 <- lmer (Perspective.response~dummy_img+Scene_C+imgscene_int+Gender_C*Face_gender_C+(dummy_img|participant),data= interaction.df)
out.fit_scene2<- lmer (help.response~dummy_img+Scene_C+Perspective_C+imgscene_int+Gender_C*Face_gender_C+(dummy_img+Perspective_C|participant),data= interaction.df) med.out_scene <- mediate (med.fit_scene2, out.fit_scene2, treat='imgscene_int', mediator = 'Perspective_C')
summary(Mod.Med_sceneest);summary(Mod.Med_sceneimg);summary(med.out_scene)
summary(med.fit_scene);summary(out.fit_scene)
#use to plot path a
est_scenepersp<- lmer (Perspective.response~Scene_C+Gender_C*Face_gender_C+(Scene_C|participant),data= subset(interaction.df,Condition=="Estimate"))
img_scenepersp<- lmer (Perspective.response~Scene_C+Gender_C*Face_gender_C+(Scene_C|participant),data= subset(interaction.df,Condition=="Imagine"))
summary(est_scenepersp);summary(img_scenepersp)
```


#Multilevel factor analysis
removed intrigued and intent.
Have a 2 factor model with distress and empathy
```{r}
emotion_num <- c(16,18,20,22,24,26,28,30,32,34)
emoFA.df<- data.frame ('participants'=IPEF.df$participant, IPEF.df[emotion_num])
mcfa_emotreact<- mcfa.input('participants',emoFA.df)
twofactor <- 'Empathy =~ softhearted.response+warm.response+sympathetic.response+
                        compassionate.response+tender.response+moved.response; 
              Distress=~ troubled.response+distressed.response+disturb.response+worried.response'
result1_emotreact<- cfa(twofactor, sample.cov=mcfa_emotreact$pw.cov, sample.nobs=mcfa_emotreact$n-mcfa_emotreact$G )
summary(result1_emotreact,fit.measures=T, standardized=T)
twofactor_loading_emot<-lavPredict(result1_emotreact, newdata=emoFA.df)
emotreact.df<- IPEF.df
emotreact.df <- cbind(emotreact.df, twofactor_loading_emot)
```

##Data preparation
```{r}
emotreact.df<- emotreact.df%>% 
                      mutate(
                        Empathy_C=group_center(Empathy, participant),
                        Distress_C=group_center(Distress, participant),
                        Empathy_M=means(Empathy, participant),
                        Distress_M=means(Distress, participant),
                        Empathy_MC= Empathy_M-mean(unique(emotreact.df$Empathy_M)),
                        Distress_MC= Distress_M-mean(unique(emotreact.df$Distress_M))
                        )
#create data with 1v2
emotreact.df1v2<- emotreact.df[emotreact.df$Condition!='Identify',]
emotreact.df1v2$Condition<- droplevels(emotreact.df1v2$Condition)
emotreact.df1v2<- emotreact.df1v2%>% 
                      mutate(
                        Empathy_C=group_center(Empathy, participant),
                        Distress_C=group_center(Distress, participant),
                        Empathy_M=means(Empathy, participant),
                        Distress_M=means(Distress, participant),
                        Empathy_MC= Empathy_M-mean(unique(emotreact.df$Empathy_M)),
                        Distress_MC= Distress_M-mean(unique(emotreact.df$Distress_M))
                        )
#create data with 0v2
emotreact.df0v2<- emotreact.df[emotreact.df$Condition!='Estimate',]
emotreact.df0v2$Condition<- droplevels(emotreact.df0v2$Condition)
emotreact.df0v2<- emotreact.df0v2%>% 
                      mutate(
                        Empathy_C=group_center(Empathy, participant),
                        Distress_C=group_center(Distress, participant),
                        Empathy_M=means(Empathy, participant),
                        Distress_M=means(Distress, participant),
                        Empathy_MC= Empathy_M-mean(unique(emotreact.df$Empathy_M)),
                        Distress_MC= Distress_M-mean(unique(emotreact.df$Distress_M))
                        )
```

##2 factor models: Empathy MLM. 
###Empathy
```{r}
#Empathy: confirmatory 1v2
empathy_zcp<- lmer(help.response~Condition*Empathy_MC+Empathy_C+(dummy_img||participant)+(dummy_img*Empathy_MC||Story_ID), data= emotreact.df1v2)
empathy_step<- step(empathy_zcp) #Retain dummy_img in participants
empathy_rm<- lmer(help.response~Condition*Empathy_MC+Empathy_C+(dummy_img||participant)+(1|Story_ID), data= emotreact.df1v2)
##Final model
empathy_final<- lmer(help.response~Condition*Empathy_MC+Empathy_C+(dummy_img|participant)+(1|Story_ID), data= emotreact.df1v2)
empathy_final<- update(empathy_final, .~., start= getME(empathy_final, 'theta')) #one refit
anova(empathy_rm,empathy_final, refit=F)
anova(empathy_final, test='kenward-roger')
summary(empathy_final)

#Empathy: Exploratory 0v2
empathy_zcp2<- lmer(help.response~Condition*Empathy_MC+Empathy_C+(dummy_img||participant)+(dummy_img*Empathy_MC||Story_ID), data= emotreact.df0v2)
empathy_step2<- step(empathy_zcp2) #retain dummy_img in participant
empathy_rm2<- lmer(help.response~Condition*Empathy_MC+Empathy_C+(dummy_img||participant)+(1|Story_ID), data= emotreact.df0v2)
##Final model
empathy_final2<- lmer(help.response~Condition*Empathy_MC+Empathy_C+(dummy_img|participant)+(1|Story_ID), data= emotreact.df0v2)
empathy_final2<- update(empathy_final2, .~., start= getME(empathy_final2, 'theta')) #2 refit 
anova(empathy_rm2,empathy_final2, refit=F)
anova(empathy_final2, test='kenward-roger')
summary(empathy_final2)
```

###Distress
```{r}
#Distress: confirmatory 1v2
distress_zcp1<- lmer(help.response~Condition*Distress_MC+Distress_C+(dummy_img||participant)+(dummy_img*Distress_MC||Story_ID), data= emotreact.df1v2)
distress_step1<-step(distress_zcp1) #retain dummy_img in participant
distress_rm<- lmer(help.response~Condition*Distress_MC+Distress_C+(dummy_img||participant)+(1|Story_ID), data= emotreact.df1v2)
#Final
distress_final<- lmer(help.response~Condition*Distress_MC+Distress_C+(dummy_img|participant)+(1|Story_ID), data= emotreact.df1v2) 
anova(distress_final, test='kenward-roger')
summary(distress_final)

#Distress: exploratory 0v2
distress_zcp2<- lmer(help.response~Condition*Distress_MC+Distress_C+(dummy_img||participant)+(dummy_img*Distress_MC||Story_ID), data= emotreact.df0v2)
distress_step2<-step(distress_zcp2) #retain dummy_img in participant
distress_rm<- lmer(help.response~Condition*Distress_MC+Distress_C+(dummy_img||participant)+(1|Story_ID), data= emotreact.df0v2)
#Final
distress_final<- lmer(help.response~Condition*Distress_MC+Distress_C+(dummy_img|participant)+(1|Story_ID), data= emotreact.df0v2) 
anova(distress_final, test='kenward-roger')
summary(distress_final)
```


#IRI ratings
```{r}
#Confirmatory analysis: 1v2
#Perspective taking
IRIPT_zcp<- lmer(help.response~Condition*IRIPerspective_GMC+(dummy_img||participant)+(dummy_img*IRIPerspective_GMC||Story_ID), data= subset(IPEF.df,Condition!="Identify"))
step(IRIPT_zcp) #Retain dummy_img in participants
IRIPT_rm<- lmer(help.response~Condition*IRIPerspective_GMC+(dummy_img||participant)+(1|Story_ID), data= subset(IPEF.df,Condition!="Identify"))
#Final 
IRIPT_final<- lmer(help.response~Condition*IRIPerspective_GMC+(dummy_img|participant)+(1|Story_ID), data= subset(IPEF.df,Condition!="Identify"))
anova(IRIPT_final, test='kenward-roger');summary(IRIPT_final)
#Emotional concern: confirmatory 1v2
IRIEC_zcp<- lmer(help.response~Condition*IRIEmotional_GMC+(dummy_img||participant)+(dummy_img*IRIEmotional_GMC||Story_ID), data= subset(IPEF.df,Condition!="Identify"))
step(IRIEC_zcp) #Retain dummy_img in participants
IRIEC_rm<- lmer(help.response~Condition*IRIEmotional_GMC+(dummy_img||participant)+(1|Story_ID), data= subset(IPEF.df,Condition!="Identify"))
#Final 
IRIEC_final<- lmer(help.response~dummy_img*IRIEmotional_GMC+(dummy_img|participant)+(1|Story_ID), data= subset(IPEF.df,Condition!="Identify"))
anova(IRIEC_rm, IRIEC_final, refit = F)
anova(IRIEC_final, test='kenward-roger');summary(IRIEC_final)
#Distress: confirmatory 1v2
IRIDS_zcp<- lmer(help.response~Condition*IRIDistress_GMC+(dummy_img||participant)+(dummy_img*IRIDistress_GMC||Story_ID), data= subset(IPEF.df,Condition!="Identify"))
step(IRIDS_zcp) #Retain dummy_img in participants
IRIDS_rm<- lmer(help.response~Condition*IRIDistress_GMC+(dummy_img||participant)+(1|Story_ID), data= subset(IPEF.df,Condition!="Identify"))
#Final 
IRIDS_final<- lmer(help.response~Condition*IRIDistress_GMC+(dummy_img|participant)+(1|Story_ID), data= subset(IPEF.df,Condition!="Identify"))
anova(IRIDS_rm, IRIDS_final, refit = F)
anova(IRIDS_final, test='kenward-roger');summary(IRIDS_final)
#Fantasy: confirmatory 1v2
IRIFY_zcp<- lmer(help.response~Condition*IRIFantasy_GMC+(dummy_img||participant)+(dummy_img*IRIFantasy_GMC||Story_ID), data= subset(IPEF.df,Condition!="Identify"))
step(IRIFY_zcp) #Retain dummy_img in participants
IRIFY_rm<- lmer(help.response~Condition*IRIFantasy_GMC+(dummy_img||participant)+(1|Story_ID), data= subset(IPEF.df,Condition!="Identify"))
#Final 
IRIFY_final<- lmer(help.response~Condition*IRIFantasy_GMC+(dummy_img|participant)+(1|Story_ID), data= subset(IPEF.df,Condition!="Identify"))
anova(IRIFY_rm, IRIFY_final, refit = F)
anova(IRIFY_final, test='kenward-roger');summary(IRIFY_final)
````
````{r}
#Exploratory analysis: 0v2
#Perspective taking
IRIPT_zcp1<- lmer(help.response~Condition*IRIPerspective_GMC+(dummy_img||participant)+(dummy_img*IRIPerspective_GMC||Story_ID), data= subset(IPEF.df,Condition!="Estimate"))
step(IRIPT_zcp1) #Retain dummy_img in participants
IRIPT_rm1<- lmer(help.response~Condition*IRIPerspective_GMC+(dummy_img||participant)+(1|Story_ID), data= subset(IPEF.df,Condition!="Estimate"))
#Final 
IRIPT_final1<- lmer(help.response~Condition*IRIPerspective_GMC+(dummy_img|participant)+(1|Story_ID), data= subset(IPEF.df,Condition!="Estimate"))
anova(IRIPT_rm1, IRIPT_final1, refit = F)
anova(IRIPT_final1, test='kenward-roger');summary(IRIPT_final1)
#Emotional concern: confirmatory 0v2
IRIEC_zcp1<- lmer(help.response~Condition*IRIEmotional_GMC+(dummy_img||participant)+(dummy_img*IRIEmotional_GMC||Story_ID), data= subset(IPEF.df,Condition!="Estimate"))
step(IRIEC_zcp1) #Retain dummy_img in participants
IRIEC_rm1<- lmer(help.response~Condition*IRIEmotional_GMC+(dummy_img||participant)+(1|Story_ID), data= subset(IPEF.df,Condition!="Estimate"))
#Final 
IRIEC_final1<- lmer(help.response~Condition*IRIEmotional_GMC+(dummy_img|participant)+(1|Story_ID), data= subset(IPEF.df,Condition!="Estimate"))
anova(IRIEC_rm1, IRIEC_final1, refit = F)
anova(IRIEC_final1, test='kenward-roger');summary(IRIEC_final1)
#Distress: confirmatory 0v2
IRIDS_zcp1<- lmer(help.response~Condition*IRIDistress_GMC+(dummy_img||participant)+(dummy_img*IRIDistress_GMC||Story_ID), data= subset(IPEF.df,Condition!="Estimate"))
step(IRIDS_zcp1) #Retain dummy_img in participants
IRIDS_rm1<- lmer(help.response~Condition*IRIDistress_GMC+(dummy_img||participant)+(1|Story_ID), data= subset(IPEF.df,Condition!="Estimate"))
#Final 
IRIDS_final1<- lmer(help.response~Condition*IRIDistress_GMC+(dummy_img|participant)+(1|Story_ID), data= subset(IPEF.df,Condition!="Estimate"))
anova(IRIDS_rm1, IRIDS_final1, refit = F)
anova(IRIDS_final1, test='kenward-roger');summary(IRIDS_final1)
#Fantasy: confirmatory 0v2
IRIFY_zcp1<- lmer(help.response~Condition*IRIFantasy_GMC+(dummy_img||participant)+(dummy_img*IRIFantasy_GMC||Story_ID), data= subset(IPEF.df,Condition!="Estimate"))
step(IRIFY_zcp1) #Retain dummy_img in participants
IRIFY_rm1<- lmer(help.response~Condition*IRIFantasy_GMC+(dummy_img||participant)+(1|Story_ID), data= subset(IPEF.df,Condition!="Estimate"))
#Final 
IRIFY_final1<- lmer(help.response~Condition*IRIFantasy_GMC+(dummy_img|participant)+(1|Story_ID), data= subset(IPEF.df,Condition!="Estimate"))
anova(IRIFY_rm1, IRIFY_final1, refit = F)
anova(IRIFY_final1, test='kenward-roger');summary(IRIFY_final1)
```





